Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-29 thesis/results.tex
Add analysis of stream and pseudo code algorithm

These statistics don't suggest much, the minimum size and 1st quartile
represent the presence of empty packets typically sent to create and destroy
connections as well as acknowledge received data. The 3rd quartile and maximum
sizes represent the maximum transmission unit for the Ethernet specification
(TODO: ref). Only the median and mean statistics suggest any difference, with
Tor traffic showing a possible preference for slightly smaller packets.
Representing each phase as a histogram however, shows a very clear distinction
between regular and Tor traffic.

@@

>>>>

These statistics don't suggest much, the minimum size and 1st quartile
represent the presence of empty packets typically sent to create and destroy
connections as well as acknowledge received data. The 3rd quartile and maximum
sizes represent the maximum transmission unit for the Ethernet specification
\parencite{Postel:1988fk}. Only the median and mean statistics suggest any
difference, with Tor traffic showing a possible preference for slightly smaller
packets.  Representing each phase as a histogram however, shows a very clear
distinction between regular and Tor traffic.

@@

Investigating more closely, by examining individual packet traces some
significant patterns begin to appear. Table \ref{table:packet_sizes} shows the
packet sizes seen for the first 10 packets of a 1\% sample of sessions in each
phase of data captured. The first few packets contain 0 bytes of data, these
are the typical SYN, SYN/ACK and ACK flagged packets that are used to initiate
a TCP/IP connection. Following that only two packet sizes are seen for HTTP
connections 100 and 110. For Tor sessions a range of packet sizes from 131 to
152. This knowledge can be used to build a very rudimentary classification
algorithm to identify Tor traffic, as seen in the pseudo-code below:

\begin{lstlisting}[language=ruby]
if packet[3] > 130 && packet[3] <  153 && packet[5] > 913 && packet[5] < 937
  is_tor = true
else
  is_tor = false
end
\end{lstlisting}

Applying this algorithm to a 10\% sample of each of the packet traces yields
the results as seen in table \ref{table:heuristic-results}.

\begin{table}[H]
  \begin{tabular}{lr}
    \toprule
    Protocol & Identified as Tor\\
    \midrule
    HTTPS & 0.0000\% \\
    HTTP over Tor & 0.9903\% \\
    HTTPS over Tor & 0.9826\% \\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:heuristic-results}
\end{table}

\begin{table}[H]
  \begin{tabular}{lp{14cm}}
    \toprule
    Index in Stream & Observed Packet Sizes\\
    \midrule
    HTTPS\\
    \midrule
    0 & 0\\
    1 & 0\\
    2 & 0\\
    3 & 100, 110\\
    4 & 0\\
    5 & 122, 516\\
    6 & 0\\
    7 & 6, 139\\
    8 & 0, 6, 37\\
    9 & 0, 37, 459, 465, 471, 514, 515\\
    10 & 0, 37, 417, 418, 419, 429, 436, 438, 439, 447, 448, 449, 454, 459, 463, 464, 465, 466, 470, 471, 486, 497, 499, 512, 513, 514, 523\\
    \midrule
    HTTP Over Tor\\
    \midrule
    0 & 0\\
    1 & 0\\
    2 & 0\\
    3 & 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 143, 144, 145, 146, 147, 148, 149, 150, 151, 152\\
    4 & 0\\
    5 & 915, 916, 917, 918, 919, 920, 921, 922, 923, 924, 925, 926, 927, 928, 929, 930, 931, 932, 933, 934\\
    6 & 0\\
    7 & 198\\
    8 & 0, 250, 266\\
    9 & 0, 250, 266, 293, 309, 325\\
    10 & 0, 293, 309, 325, 1448\\
    \midrule
    HTTPS Over Tor\\
    \midrule
    0 & 0\\
    1 & 0\\
    2 & 0\\
    3 & 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 144, 145, 146, 147, 148, 149, 150, 151, 152\\
    4 & 0\\
    5 & 914, 915, 916, 918, 919, 920, 921, 922, 923, 925, 926, 927, 928, 929, 930, 932, 934, 935, 936\\
    6 & 0\\
    7 & 197, 198\\
    8 & 0, 250, 266\\
    9 & 0, 250, 266, 293, 309, 325\\
    10 & 0, 293, 309, 325, 1448\\
    \bottomrule
  \end{tabular}
  \caption{Packet sizes}
  \label{table:packet_sizes}
\end{table}
